### 2017-11-24 Chapter1/feedback.tex
Latest on 24/11/2017

	To illustrate the different types of feedback we will take help of the following example. Let a learner be given a set of actions $i\in\A$ such that $|A|=K$. Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$. The learning proceeds as follows:-

\begin{algorithm}[!th]
\caption{An online sequential game}
\label{alg:OSeqGame}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The environment chooses a reward $r_{i,t},\forall i\in\A$.
\State The learner chooses $m$ actions such that $m < K$, where $A$ is the set of arms and $|A|=K$.
\State The learner observes the reward $R_{m,t}=F\left( r_{i,t}\right)$.
\State \EndFor
\end{algorithmic}
\end{algorithm}

@@

\subsection{Full information feedback}
In full information feedback, when a learner selects $m$ actions then the environment reveals the rewards of all the actions $i\in \A$. Hence, in this form of feedback  the learner observes $R_{m,t} = \lbrace r_{i,t},\forall i\in\A\rbrace$.

\subsection{Partial information feedback}
In partial information feedback, when a learner selects $m$ actions then the environment reveals the rewards of only those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R_{m,t} = \lbrace r_{m,t},\forall m\in\A\rbrace$. This is also sometimes called the semi-bandit feedback.

\subsection{Bandit feedback}
In bandit feedback, when a learner selects $m$ actions then the environment reveals a cumulative reward of those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R_{m,t} = \sum_{q=1}^{m} r_{q,t}$. Note, that when $m=1$, then the learner observes the reward of only that action that it has chosen out of $K$ actions.

>>>>

	To illustrate the different types of feedback we will take help of the following example. Let a learner be given a set of finite actions $i\in\A$ such that $|\A|=K$. Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$. The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $R^{obs}_{t}$ (which will be characterized later). Before the learner selects the  the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback. This game is shown in algorithm \ref{alg:OSeqGame}.

\begin{algorithm}[!th]
\caption{An online sequential game}
\label{alg:OSeqGame}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
\State The learner chooses $m$ actions such that $m < K$, where $\A$ is the set of arms and $|\A|=K$.
\State The learner observes the reward vector $R^{obs}_{t}\subseteq F^{env}_{t}$.
\State \EndFor
\end{algorithmic}
\end{algorithm}

@@

\subsection{Full information feedback}
In full information feedback, when a learner selects $m$ actions then the environment reveals the rewards of all the actions $i\in \A$. Hence, in this form of feedback  the learner observes $R^{obs}_{t} = F^{env}_{t}=[r_{i,t},\forall i\in\A]$. This has been studied in many forms previously in \citet{takimoto2003path}, \citet{kalai2005efficient} or in online prediction with full information feedback in \citet{cesa2006prediction}.

\subsection{Partial information feedback}
In partial information feedback, when a learner selects $m$ actions then the environment reveals the rewards of only those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R^{obs}_{t} = [ r_{m,t},\forall m\in\A ]$. This is also sometimes called the semi-bandit feedback and has been studied in \citet{awerbuch2004adaptive},   \citet{mcmahan2004online} and \citet{gyorgy2007line}.

\subsection{Bandit feedback}
In bandit feedback, when a learner selects $m$ actions then the environment reveals a cumulative reward of those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R^{obs}_{t} = \sum_{q=1}^{m} r_{q,t}$. Note, that when $m=1$, then the learner observes the reward of only that action that it has chosen out of $K$ actions. Bandit feedback for single action has been extensively studied in literature with many open problems and we focus on its various interpretations in this thesis.

### 2017-11-24 Chapter1/motivation.tex
Latest on 5/11/2017
Latest on 24/11/2017

The MAB model fits very well in various real-world scenarios that can be modeled as sequential decision-making problems. Some of which are mentioned as follows:-
\begin{enumerate}
\item \emph{Online Shop Domain (\cite{ghavamzadeh2015bayesian}):} In the online shop domain, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers. In this scenario, at every timestep,  the retailer displays an item to a customer from a pool of items which has the highest probability of being selected by the customer. The episode ends when the customer selects or does not select a product (which will be considered as a loss to the retailer) and the process is again repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display the next item.
\item \emph{Medical Treatment Design (\cite{thompson1933likelihood}):} Here at every timestep, the agent chooses to administer one out of several treatments sequentially on a patient. Here, the episode ends when the patient responds well or does not respond well to the treatment whereby the agent modifies its policy for the next suggestion.
\item \emph{Financial Portfolio Management:} In financial portfolio management MAB model can be used. Here, the agent is faced with the choice of selecting the most profitable stock option out of several stock options. The simplest strategy where we can employ a bandit model is this; at the start of every trading session the agent suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading. The  profit recorded is treated as the reward revealed by the environment and the agent modifies its policy for the next day.
%\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase. In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase. So from the several variants of the product that are in the test phase the learning agent must suggest a product variant at the end of the test phase that has the highest probability of minimizing loss in the commercialization phase(see \cite{bubeck2011pure}). 
%\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications (\cite{audibert2009exploration}). Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learning algorithm has to explore as many channels as possible to suggest the best possible channel. Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible suggestion within a very small  number of attempts. 
\end{enumerate}

	The thresholding bandit problem is a special case of combinatorial MAB problem where the learner has to suggest the best set of arms above a real valued threshold. This has several relevant industrial applications. The variants of TopM problem (identifying the best $M$ arms from $K$ given arms) can be readily used in the thresholding problem.

\begin{enumerate}
\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase. In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase. So from the several variants of the product that are in the test phase the learning agent must suggest the product variant(s) that are above a particular threshold $\tau$ at the end of the test phase that have the highest probability of minimizing loss in the commercialization phase. A similar problem has been discussed for single best product variant identification without threshold in \cite{bubeck2011pure}. 
\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications (\cite{audibert2009exploration}). Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learning algorithm has to explore as many channels as possible to suggest the best possible set of channel(s) that are above a particular threshold $\tau$. The threshold depends on the subscription level of the customer. With higher subscription the customer is allowed better channel(s) with the $\tau$ set high. Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible suggestion within a very small  number of attempts.
\item \emph{Anomaly Detection and Classification:} Thresholding bandit can also be used for anomaly detection and classification where we define a cutoff level $\tau$ and for any samples above this cutoff gets classified as an anomaly. For further reading we point the reader to section 3 of \cite{locatelli2016optimal}.
\end{enumerate}

	In all the above examples the MAB model performs well mainly because all of them suffer from \textit{exploration-exploitation dilemma}. This is characterized by action-selection choice faced by the agent where it must decide whether to stay with the action yielding highest reward till now or to explore newer actions which might be more profitable in the long run. MAB's are suited for such scenarios because 
\begin{enumerate}
\item They are easy to implement.
\item The switch between exploration and exploitation is more well defined theoretically.
\item They perform well empirically.
\end{enumerate}

>>>>

The MAB model fits very well in various real-world scenarios that can be modeled as sequential decision-making problems. Some of which are mentioned as follows:-
\begin{enumerate}
\item \emph{Online Shop Domain:} In the online shop domain \cite{ghavamzadeh2015bayesian}, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers. In this scenario, at every timestep, the retailer displays an item to a customer from a pool of items which has the highest probability of being selected by the customer. The episode ends when the customer selects or does not select a product (which will be considered as a loss to the retailer). This feedback is incorporated by the learner as a feedback from the environment and it modifies its policy for the next suggestion. This process is repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display other items to different customers.
\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \cite{thompson1933likelihood},\cite{thompson1935theory}. Here at every timestep, the learner chooses to administer one out of several treatments sequentially on a stream of patients who are suffering from the same ailment (say). Let's also assume that there is a single treatment which will be able to alleviate the patients from their disease. Here, the episode ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient. The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relive the patient of its ailment with a high probability.
\item \emph{Financial Portfolio Management:} In financial portfolio management MAB models can also be used. Here, the learner is faced with the choice of selecting the most profitable stock option out of several stock options. The simplest strategy where we can employ a bandit model is this; at the start of every trading session the learner suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading. The  profit recorded is treated as the reward revealed by the environment and the learner modifies its policy for the next day. Let's assume that no new stock options are being introduced over the considered time horizon and there is a single best stock option which if selected for perpetuity will always give the best returns. Then, the goal of the learner is reduced to identifying the best stock option as quickly as possible. 
\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase. In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase. So from the several variants of the product that are in the test phase the learning learner must suggest the product variant(s) whose qualities are above a particular threshold $\tau$ at the end of the test phase that have the highest probability of minimizing loss in the commercialization phase. A similar problem has been discussed for single best product variant identification without threshold in \citet{bubeck2011pure}. 
\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications \citep{audibert2009exploration}. Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learner has to explore as many channels as possible to suggest the best possible set of channel(s) whose qualities are above a particular threshold $\tau$. The threshold may depend on the subscription level of the customer such that with higher subscription the customer is allowed better channel(s) with the $\tau$ set high. Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible set of suggestions within a very small  number of attempts.
\item \emph{Anomaly Detection and Classification:} MABs can also be used for anomaly detection where the goal is to seek out extreme values in the data. Anomalies may not always be naturally concentrated which was shown in  \citet{steinwart2005classification}. To implement a MAB model the best possible way is to define a cut-off level $\tau$ and classify the samples above this level $\tau$ as anomalous along with a tolerance factor which gives it a degree of flexibility. Such an approach has already been mentioned in \citet{streeter2006selecting} and further studied in \citet{locatelli2016optimal}.
\end{enumerate}

%	In all the above examples the MAB model performs well mainly because all of them suffer from \textit{exploration-exploitation dilemma}. This is characterized by action-selection choice faced by the learner where it must decide whether to stay with the action yielding highest reward till now or to explore newer actions which might be more profitable in the long run. MAB's are suited for such scenarios because 
%\begin{enumerate}
%\item They are easy to implement.
%\item The switch between exploration and exploitation is more well defined theoretically.
%\item They perform well empirically.
%\end{enumerate}

### 2017-11-24 Chapter1/types.tex
Latest on 24/11/2017

\begin{itemize}
\item \textbf{Adversarial bandits: } In adversarial bandits, an adversary decides the payoff for each arm before the learner selects an arm. This adversary may or may not be oblivious to the learning algorithm employed by the learner. In each of these cases a different guarantee on the performance of the learner can be arrived at. Some of the important papers in this setting are \citet{auer2002nonstochastic}, \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.

\item \textbf{Piece-wise stationary:} Another setup under this setting can be the piece-wise stationary setting. In this setting, the distribution associated with each arm is not fixed throughout the time horizon and changes either arbitrarily at particular changepoints, or changes at a fixed period. The distribution associated with each arm then  remains fixed till the next chnagepoint is encountered. Chapter (to be added) is based on this.
\end{itemize}

@@

\subsubsection{Cumulative regret minimization}

\subsubsection{Simple regret minimization}

\subsubsection{External Regret minimization}

@@

>>>>

\begin{itemize}
\item \textbf{Adversarial bandits: } In adversarial bandits, an adversary decides the payoff for each arm before the learner selects an arm. This adversary may or may not be oblivious to the learning algorithm employed by the learner. In each of these cases a different guarantee on the performance of the learner can be arrived at. Some of the important papers in this setting are \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.

\item \textbf{Piece-wise stationary:} Another setup under this setting can be the piece-wise stationary setting. In this setting, the distribution associated with each arm is not fixed throughout the time horizon and changes either arbitrarily at particular changepoints, or changes at a fixed period. The distribution associated with each arm then  remains fixed till the next chnagepoint is encountered. Several recent works have focussed on this such as  \citep{garivier2011upper}, \citep{mellor2013thompson}, and \citep{allesiardo2017non}. In our thesis, chapter \ref{chap:psbandit} is based on this setting. 
\end{itemize}

@@

In bandit literature, based on the goal we can divide bandits into several categories. To illustrate his we put forward a simple scenario let us consider a stochastic bandit scenario where there are $K$ arms labeled $i=1,2,\ldots,K$ with their expected means of reward distributions ($D_i$) be denoted by $r_i$. Also let there be single optimal arm $*$ such that $r^* = \max_{i\in\A}r_i$.

\subsubsection{Cumulative regret minimization}
In cumulative regret minimization the goal of the bandit is to minimize the cumulative regret which is the total loss suffered by the learner throughout the time horizon $T$ for not choosing the optimal arm. Formally, we can define the cumulative regret as,

\begin{eqnarray}
R_{T} = \sum_{t=1}^{T}r^* - \sum_{i\neq *}r_{i}n_{i,T} \label{eqn:chap1:regret}
\end{eqnarray}

where, $n_{i,T}$ is the number of times the learner has chosen arm $i$ over the entire horizon $T$. We can further reduce equation \ref{eqn:chap1:regret} to obtain,

\begin{align*}
R_{T} = \sum_{t=1}^{T}r^* - \sum_{i\neq *}r_{i}n_{i,T} = \sum_{i=1}^{K}\Delta_{i}n_{i,T}
\end{align*}

where $\Delta_{i}=r^* - r_i$ is called the gap between the optimal and the sub-optimal arm.

\subsubsection{Simple regret minimization}
In simple regret minimization the goal of the bandit is to minimize the instantaneous regret that is suffered at any  timestep by the learner. Formally, the simple regret at $t$-th timestep where $J_n\in\A$ is the recommendation by the learner at timestep $t$ is defined,

\begin{align*}
SR_{t} = r^* - r_{J_{n}} = \Delta_{J_n}
\end{align*}

where, $\Delta_{J_n}$ is the instantaneous gap between the expected mean of he optimal arm and the recommended arm by the learner.

\subsubsection{Weak Regret minimization}
In the non-stochastic scenario, when the distribution associated with each arm changes, the notion of regret is defined differently than cumulative regret. In this scenario, considering that there is a single best arm, the learner is more interested in minimizing the worst-case regret. Formally, for any sequence of actions $\left( j_1, \ldots , j_T \right)$ over the time horizon $T$, the weak regret for single best action is defined as the difference between,
\begin{align*}
G_{\max}(j_1,\ldots,j_T) - G_{\pi}(T)
\end{align*}
where, $G_{\max}(j_1,\ldots,j_T) = \max_{i\in\A}\sum_{t=1}^{T}x_{i_t}$ is the return of the globally best action over the entire horizon $T$ and $G_{\pi}(T)$ is the return following the policy $\pi$ over the horizon $T$ instead of choosing $j_1,\ldots,j_T$.

@@

\subsection{Bandits with Corrupt Feedback}

\subsection{Conservative Bandits}

### 2017-11-24 Chapter4/prevRes.tex
Latest on 24/11/2017

Here the learning algorithm has to suggest the best arm(s) within a fixed time-horizon $T$, that is usually given as an input. The objective is to maximize the probability of returning the best arm(s).  This is the scenario we consider in this chapter. Some of the important algorithms used in pure exploration setting are discussed in the next part.

@@

\begin{algorithm}[!h]
\caption{UCBE}
\label{alg:ucbe}
\begin{algorithmic}[1]
\State \textbf{Input: } The budget $T$
\State Pull each arm once
\For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{a}{n_i}}\bigg\rbrace$, where $a = \dfrac{25(T-K)}{36 H_1}$ and $H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}$.
\State $t:=t+1 $
\EndFor
\end{algorithmic}
\end{algorithm}

In \citet{audibert2010best} the authors propose the  UCBE and the Successive Reject (SR) algorithm, and prove simple-regret guarantees for the problem of identifying the single best arm.  In the combinatorial fixed budget setup \citet{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best $m$ arms at the end of the time budget.

@@

\begin{algorithm}[h!]
\caption{Successive Reject(SR)}
\label{alg:sr}
\begin{algorithmic}[1]
\State \textbf{Input: } The budget $T$
\State \textbf{Initialization: } $n_0 = 0$
\State \textbf{Definition: } $\bar{\log K} = \dfrac{1}{2} + \sum_{i=2}^{K}\dfrac{1}{i}$, $n_k = \dfrac{1}{\bar{\log K}}\dfrac{T-K}{K + 1 - m}$
\For{For each phase $m=1,..., K-1$}
\State For each $i \in B_{m}$, select arm $i$ for $n_k - n_{k-1}$ rounds.
\State Let $B_{m+1} = B_m\setminus \argmin_{i\in B_m} \hat{r}_i$
(remove one element from $B_m$ , if there
is a tie, select randomly the arm to dismiss among the worst arms).
\State $m:=m+1 $
\EndFor
\State Output the single remaining $i\in B_{m}$.
\end{algorithmic}
\end{algorithm}

>>>>

Here the learning algorithm has to suggest the best arm(s) within a fixed budget or time-horizon $T$, that is given as an input. The objective is to maximize the probability of returning the best arm(s).  This is the scenario we consider in this chapter. Some of the important algorithms used in pure exploration setting are discussed in the next part.

@@

One of the first algorithms proposed for the fixed budget setting is the UCB-Exploration (UCBE) algorithm in \citet{audibert2010best} used for identifying a single best arm. This is shown in algorithm \ref{alg:ucbe}.

\begin{algorithm}[!ht]
\caption{UCBE}
\label{alg:ucbe}
\begin{algorithmic}[1]
\State \textbf{Input: } The budget $T$, exploration parameter $a$
\State Pull each arm once
\For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{a}{n_i}}\bigg\rbrace$, where $a = \dfrac{25(T-K)}{36 H_1}$ and $H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}$.
\State $t:=t+1 $
\EndFor
\end{algorithmic}
\end{algorithm}

This algorithm is quite similar to the UCB1 algorithm discussed in \citet{auer2002finite} (see algorithm \ref{alg:ucb1}). The major difference between the two algorithms is the confidence interval such that for UCB1 it is designed for minimizing the cumulative regret but for UCBE it is designed for minimizing simple regret. An illustrative table comparing the two is provided in table \ref{table:comp-exp}.

\begin{table}
\caption{Confidence interval and exploration parameters of different algorithms}
\label{table:comp-exp}
\begin{center}
\begin{tabular}{|p{5em}|p{6em}|p{8em}|p{12em}|}
\hline
Algorithm  &  Confidence interval & Exploration Parameter$(a)$ & Remarks \\
\hline
\hline
UCB1       & $\sqrt{\dfrac{a}{n_i}}$ & \begin{align*}a = 2\log (t)\end{align*} & $a$ is logarithmic in $t$ to minimize cumulative regret. This achieves a balance between exploration and exploitation. Hence, the cumulative regret grows logarithmically with $t$. \\%\midrule
\hline
\hline
UCBE       & $\sqrt{\dfrac{a}{n_i}}$ & \begin{align*}a = \dfrac{25(T-K)}{36 H_1},\\ \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}\end{align*} & $a$ is linear in $T$ to minimize simple regret. Here, the main concern is to minimize the probability of error at the end of budget $T$ and conduct as much exploration as possible. Hence, a large $a$ helps to reach exponentially low probability of error.\\\midrule
\end{tabular}
\end{center}
\end{table}

@@

The Successive Reject (SR) algorithm has also been proposed in \citet{audibert2010best} and is used for identifying a single best arm. This algorithm is quite different than upper confidence bound based algorithms because it does not rely on any explicit confidence interval to select arm at every timestep. It is shown in algorithm \ref{alg:sr}.

\begin{algorithm}[!th]
\caption{Successive Reject(SR)}
\label{alg:sr}
\begin{algorithmic}[1]
\State \textbf{Input: } The budget $T$
\State \textbf{Initialization: } $n_0 = 0$
\State \textbf{Definition: } $\bar{\log K} = \dfrac{1}{2} + \sum_{i=2}^{K}\dfrac{1}{i}$, $n_k = \dfrac{1}{\bar{\log K}}\dfrac{T-K}{K + 1 - m}$
\For{For each phase $m=1,..., K-1$}
\State For each $i \in B_{m}$, select arm $i$ for $n_k - n_{k-1}$ timesteps.
\State Let $B_{m+1} = B_m\setminus \argmin_{i\in B_m} \hat{r}_i$
(remove one element from $B_m$ , if there
is a tie, select randomly the arm to dismiss among the worst arms).
\State $m:=m+1 $
\EndFor
\State Output the single remaining $i\in B_{m}$.
\end{algorithmic}
\end{algorithm}

From algorithm \ref{alg:sr} we see that SR is a round based algorithm quite similar to UCB-Improved (see algorithm \ref{alg:ucbi}). Similar to UCB-Improved, SR pulls all arms equal number of times in each round and then discards some arm that it deems to be sub-optimal until it is left with a single best arm. However, SR does not have any explicit confidence interval as UCBE, rather the idea of the confidence interval is hidden in the number of pulls allocated to each arm in every round. The number of times each arm is pulled in every round, that is $n_k - n_{k-1}$ timesteps makes sure that the optimal arm is not eliminated in the $k$-th round with high probability.

In the combinatorial fixed budget setup \citet{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best $m$ arms at the end of the time budget.
